R for Clinical Study Reports and Submission

### 2021-08-29 index.Rmd
update index.Rmd

@@

```{r}
data.frame(contributors = as.character(contributors)) %>%   
  kable(format = "html") %>%
  kable_styling()
```

>>>>

```{r, eval = FALSE, include=FALSE}
bookdown::render_book("index.Rmd", "bookdown::pdf_book")
```

@@

```{r, echo = FALSE, eval = TRUE}
data.frame(contributors = as.character(contributors)) %>%   
  kable(format = "html") %>%
  kable_styling()
```
